---
title: "G-CRT_simulation"
output: html_document
date: "2023-12-11"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning = FALSE,message = FALSE)
```

## Conditional independence testing simulation

On this page,we take an example to evaluate the numerical performance of our proposed G-CRT (Algorithm 4) with the statistic functions discussed in Section 4.3 for testing conditional independence. We employ a linear regression model for $\mathcal{L}(Y\mid X)$ with a low-dimension setting ($p=20$ and $n=50$) and fix the procedure parameters $M=100$ and $L=3$ for conducting Algorithm 2.

```{r}
library(glmnet)
library(rags2ridges)
library(glasso)
library(Matrix)
library(MASS)
library(mvtnorm)
library(reshape)
library(ggplot2)
source("CRT-Simulate.R")
source("CRT-Stat.R")
source("DBL_GLMs_functions.R")
source("OneExp.R")
source("Run-Testing.R")
source("dCRT_function.R")
source("GoF-Settings.R")
source("CSS-GGM.R")
source("GGMTesting.R")
source("CIT_function_for_webpage.R")
```

In this setting, we examine our G-CRT procedure with the statistics LM-SST and LM-SSR by comparison to the classical F-test and the Bonferroni-adjusted dCRT using Gaussian Lasso models.

```{r}
# Set parameters
popul_param_llw <- list(
  setting = "l_l_w",
  N = c(50),
  P = c(20),
  setT=1:8, 
  modelParam = list(
    K = 6,
    s = 0.2,
    grid_signal= seq(0,2.5,by=0.25)
  )
)

```

Repeat experiments 10 times

```{r}
path_prefix=paste0('Experiments-llw','/')
if(!dir.exists(path_prefix)){
  dir.create(path_prefix)
}

# Repeat experiment and save results
for (epo in 1:10){
  output = CRT_webpage(popul_param_llw,epo = epo)
  save(output,popul_param_llw,file=paste0(path_prefix,epo,'.RData'))
}

# Load results
all_output=list()
for(epo in 1:10){
  load(file=paste0(path_prefix,epo,'.RData'))
  all_output[[epo]]=output
}

combined_pvalues=list()
for(ind.signal in 1:length(popul_param_llw$modelParam$grid_signal)){
  combined_pvalues[[ind.signal]]=t(sapply(all_output, function(v)v[[ind.signal]]$pvalues))
}
combined_pvalues=lapply(combined_pvalues,function(x)x[,-c(5)])
combined_pvalues=lapply(combined_pvalues,function(x){
  colnames(x)=c("LM-SST","LM-SSR","F-test","dCRT")
  return(x)})
```

Present the power and standard error of various testing methods in the experiment, in which power is presented against varying values of $\theta$

```{r}
Fun_SE=function(x){sd(x)/sqrt(length(x))}

pvalues_array=simplify2array(combined_pvalues)
sig.lv=0.05

power_table=data.frame(apply(pvalues_array<sig.lv, 3:2,mean)); 
power_SE_table=data.frame(apply(pvalues_array<sig.lv, 3:2,Fun_SE))

num_methods=ncol(power_table)
power_table$theta=popul_param_llw$modelParam$grid_signal
power_SE_table$theta=popul_param_llw$modelParam$grid_signal



df_melt=melt(power_table,id.vars="theta", variable_name = "Test")
df_melt$Power=df_melt$value;df_melt$value=NULL

SE_melt <- melt(power_SE_table, id.vars = "theta", variable_name = "Test")
SE_melt$SE=SE_melt$value;SE_melt$value=NULL

# Merge the data and SE data frames
merged_df <- merge(df_melt, SE_melt, by = c("theta", "Test"))
print(merged_df)
```