---
title: "MC-GoF test for GGMs"
output: html_document
date: "2023-12-11"
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning = FALSE,message = FALSE)
```

## Goodness-of-fit testing

This page provides a step-by-step guide on how to conduct the Monte Carlo goodness-of-fit (MC-GoF) test for GGMs ( Algorithm 3 in the accompanying paper).

```{r}
library(Matrix)
library(MASS)
library(mvtnorm)
library(glasso)
library(Rfast)
library(glmnet)
library(rags2ridges)
library(dplyr)
library(purrr)
source("CSS-GGM.R")
source("GoF-Statistics.R")
source("GGMTesting.R")
source("GoF-OneExp.R")
source("PostAnalysis.R")
source("GoF-Settings.R")
source("GOF_function_for_webpage.R")
```

### Looking inside the GGM function

We generate random samples X from the band graph with $(K,K_0,p,s,n)=(6,6,20, 0.2, 80)$ 

```{r}
# band graph parameters
n = 80      # number of observations
p = 20      # number of dimensions
s = 0.2     # signal magnitude
K = 6       # bandwidth of true graph
K0 = 6      # bandwidth of null graph

# setting up the true graph and null graph
true_graph=graph_band(p,K,s)
null_graph=graph_band(p,K0,s) 

sigma=true_graph$sigma
inv.sigma=true_graph$inv.sigma
G0=prec_to_adj(null_graph$inv.sigma)

# Simulate the data x
X <- simulate_data(sigma, n)
```

Sampling M exchangeable copies of X, L is the number of iterations in each Markov chain (Algorithm 2)

```{r}
CSS_sample = exchangeable_sampling(X, G0, M=100, L=3)
X_copies  = CSS_sample$X_copies
```

Choosing test statistic functions: PRC and ERC discussed in Section 3.2.1, F$_{\Sigma}$ in Section 3.2.2, GLR-$\ell_1$ in Section 3.2.3.

```{r}
# statistics
List_CSS_stat = c( "PRC_SS", "ERC_Z_SS", "F_sum", "glr_glasso")

```

Monte Carlo goodness-of-fit(MC-GoF) test for GGMs (Algorithm 3)

```{r}
test_result = GoF_test_webpage(X, X_copies, G0, List_CSS_stat)
```

Output the p-value $\mathrm{pVal}_T$ of our method and take VV and DP as baselines.

```{r}
VV_pvalue = VV_GoF(X,G0)
DP_pvalue <- Bonf_GoF(X,G0)
print(list("VV_pvalue" = VV_pvalue,
           "DP_pvalue" = DP_pvalue))
print(test_result$p_values)
```

Take statistic function PRC for example, show $T(X), T(\tilde{X}^{(1)}), T(\tilde{X}^{(2)}), \cdots, T(\tilde{X}^{(M)})$

```{r}
hist(test_result$Ttildes$PRC_SS,xlab = "PRC_Ttilde",main="Histogram of PRC_Ttilde")
abline(v=test_result$T0s["PRC_SS"],col="red")
text(test_result$T0s["PRC_SS"], 0,labels = "T0", pos = 3, col = "red")
```