---
title: "GoF_simulation"
output: html_document
date: "2023-12-11"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning = FALSE,message = FALSE)
```

## Goodness-of-fit testing simulation

On this page,we take an example to evaluate the statistical power and demonstrate the theoretically valid Type-I error control of our proposed MC-GoF testing procedure for GGMs with numerical comparisons to established methods (Section 5.1 of the accompanying paper). Throughout this section, we utilize four test statistic functions (PRC, ERC, F$_{\Sigma}$, GLR-$\ell_1$) and take $M^{1}P_{1}$ and Bonf as baseline methods. Additionally, we fix the procedure parameters $M=100$ and $L=3$ for conducting Algorithm 2.

```{r}
library(Matrix)
library(MASS)
library(mvtnorm)
library(glasso)
library(Rfast)
library(glmnet)
library(rags2ridges)
library(dplyr)
library(purrr)
source("CSS-GGM.R")
source("GoF-Statistics.R")
source("GGMTesting.R")
source("GoF-OneExp.R")
source("PostAnalysis.R")
source("GoF-Settings.R")
source("GOF_function_for_webpage.R")
```

### Type I error control

Take band graph $(K,K_0,p,s,n)=(6,6,20, 0.2, 80)$ for example

```{r}
# Parameters
param_Band_template <- list(
  model = "Band_Band",
  N = 80,
  P = 20,
  modelParam = list(
    K0 = 6,
    K = 6,
    s = 0.2
  )
)
M = 100
L = 3

```

Repeat experiments 10 times

```{r}
FlagLocalTest=F
PlatForm=(Sys.info())["sysname"]
if(FlagLocalTest&(PlatForm!="Windows")){Rprof("my_profile.out")}

path_prefix=paste0('Experiments-type_I_error','/')
if(!dir.exists(path_prefix)){
  dir.create(path_prefix)
}

# Repeat experiment and save results
for (epo in 1:10){
  output = run_experiments_epo_webpage(param_Band_template,epo, M,L,List_CSS_stat =NULL ,dir_prefix=path_prefix)
  save(output,param_Band_template,file=paste0(path_prefix,epo,'.RData'))
}

# Load results
all_output=list()
for(epo in 1:10){
  load(file=paste0('Experiments-type_I_error','/',epo,'.RData'))
  all_output[[epo]]=list(output[[1]]$p_value)
}
```

We calculate the rejection proportions and conduct the one-sample proportion test for the hypothesis that the rejection probability is no greater than $\alpha = 0.05$

```{r}
summ=read_experiments_epo(param_Band_template,all_output)
#Rejection proportion
rej.table=extract_metric(metric_name='power')[c("n","p","K0","K","s","VV","DP","PRC_SS", "ERC_Z_SS", "F_sum", "glr_glasso")]
#One-sided p-value of the one-sample proportion test
ospt.table=extract_metric(metric_name='ospt')[c("n","p","K0","K","s","VV","DP","PRC_SS", "ERC_Z_SS", "F_sum", "glr_glasso")]

table1 = rbind(rej.table,ospt.table)
rownames(table1) = c("rej.pro","ospt")
colnames(table1) = c("n","p","K0","K","s","VV","DP","PRC","ERC","F_sum","GLR_l1")
print(table1)
```

### Power comparison

Take band graph $(K,K_0,p,s,n)=(6,1,20, 0.2, 40)$ for example

```{r}
param_Band_template <- list(
  model = "Band_Band",
  N = 40,
  P = 20,
  modelParam = list(
    K0 = 1,
    K = 6,
    s = 0.1
  )
)
M = 100
L = 3
```

Repeat experiments 10 times

```{r}
path_prefix=paste0('Experiments-power-band','/')
if(!dir.exists(path_prefix)){
  dir.create(path_prefix)
}

# Repeat experiment and save results
for (epo in 1:10){
  output = run_experiments_epo_webpage(param_Band_template,epo, M,L,List_CSS_stat =NULL ,dir_prefix=path_prefix)
  save(output,param_Band_template,file=paste0(path_prefix,epo,'.RData'))
}

# Load results
all_output=list()
for(epo in 1:10){
  load(file=paste0('Experiments-power-band','/',epo,'.RData'))
  all_output[[epo]]=list(output[[1]]$p_value)
}
```

Calculate the power and standard error

```{r}
summ=read_experiments_epo(param_Band_template,all_output)
#Power
power.table=extract_metric(metric_name='power')[c("n","p","K0","K","s","VV","DP","PRC_SS", "ERC_Z_SS", "F_sum", "glr_glasso")]
#Standard error
SE.table=extract_metric(metric_name='SE')[c("n","p","K0","K","s","VV","DP","PRC_SS", "ERC_Z_SS", "F_sum", "glr_glasso")]

table2 = rbind(power.table,SE.table)
rownames(table2) = c("power","std_error")
colnames(table2) = c("n","p","K0","K","s","VV","DP","PRC","ERC","F_sum","GLR_lasso")
print(table2)
```