---
title: "Graphical_conditional_randomization_test"
output: html_document
date: "2023-12-11"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning = FALSE,message = FALSE)
```

## Conditional independence testing

This page provides a step-by-step guide on how to conduct the Graphical conditional randomization test (G-CRT) ( Algorithm 4 in the accompanying paper). Our methodology is based on a combination of the conditional randomization test [CRT](https://academic.oup.com/jrsssb/article/80/3/551/7048447) and our algorithm for generating exchangeable copies in Section 2.

```{r}
library(glmnet)
library(rags2ridges)
library(glasso)
library(Matrix)
library(MASS)
library(mvtnorm)
library(reshape)
library(ggplot2)
source("CRT-Simulate.R")
source("CRT-Stat.R")
source("DBL_GLMs_functions.R")
source("OneExp.R")
source("Run-Testing.R")
source("dCRT_function.R")
source("GoF-Settings.R")
source("CSS-GGM.R")
source("GGMTesting.R")
source("CIT_function_for_webpage.R")
```

### Looking into the CRT function

Take the Gaussian linear regression for example

```{r}
setting = "l_l_w"             # gaussian linear regression (low-dimensional setting)
n = c(50)             
p = c(20)
setT=1:8

K = 6
s = 0.2
grid_signal= seq(0,2.5,by=0.25)   # control signal strength

# get graph G
true_graph=graph_band(p,K,s)
perm.var=sample(p,p)
sigma=true_graph$sigma[perm.var,perm.var]
inv.sigma=true_graph$inv.sigma[perm.var,perm.var]
diag_s=sqrt(diag(sigma))
sigma=sweep(sweep(sigma,1,1/diag_s,"*"),2,1/diag_s, "*")
inv.sigma=sweep(sweep(inv.sigma,1,diag_s,"*"),2,diag_s, "*")
G = prec_to_adj(inv.sigma)       # graph G

# Simulate the data X
X <- simulate_data(sigma, n)
beta=random_beta(p)              # regression coefficient
noise_unif=runif(n)
```

Sampling M exchangeable copies of X, L is the number of iterations in each Markov chain (Algorithm 2)

```{r}
CSS_sample = exchangeable_sampling(X, G, I = setT, bReduced = T, M=100, L=3)
X_copies  = CSS_sample$X_copies
```

We choose statistics LM-SST and LM-SSR by comparison to the classical F-test for the null hypothesis $H_0: \beta_{\mathcal{T}}=0$ and the dCRT using a Gaussian Lasso model (Bonferroni adjusted). 

```{r}
# statistics
List_Stat_Comb=c("Stat_Comb_Linear_SST","Stat_Comb_Linear_Dev")
```

CRT test (Algorithm 4)

```{r}
test_result = GRT_test_webpage(X, CSS_sample, setting, setT, beta, niose_unif, grid_signal, List_Stat_Comb,IncludeBaseline = T)
```

Output the p-value

```{r}
for(ind.signal in 1:length(grid_signal)){
  print(paste("theta=",test_result[[ind.signal]]$theta))
  output_pvalue = test_result[[ind.signal]]$pvalues[-which(names(test_result[[ind.signal]]$pvalues)=="dCRT_RF")]
  names(output_pvalue) = c("LM-SST","LM-SSR","F-test","dCRT")
  print(output_pvalue)
}
```

Take theta = 0, statistics: LM-SST for example, show $T(Y, X), T(Y, \tilde{X}^{(1)}),  \cdots, T(Y, \tilde{X}^{(M)})$

```{r}
hist(test_result$`theta= 0`$Ttildes$Stat_Comb_Linear_SST,xlab = "LM-SST_Ttilde",main="Histogram of LM-SST_Ttilde")
abline(v=test_result$`theta= 0`$T0s$Stat_Comb_Linear_SST,col="red")
text(test_result$`theta= 0`$T0s$Stat_Comb_Linear_SST, 0,labels = "T0", pos = 3, col = "red")
```
